TBD

### 2023-03-05 outputs/paper/paper3.qmd
minor addition to TODO items
Explore relationships with income

@@

## To Do

@@

-   calculating % ... over the year for graph

@@

## Introduction

@@

@@

#### Gaps

@@

#### Translations

@@

#### Affordances: New Experiments

@@

#### Impact on our study

@@

## Findings

### Financial Satisfaction

@@

@@

financial_satisfaction_across_years_by_cohort |>
  filter(!is.na(financial_satisfaction)) |>
  filter(!(is.na(cohort_band))) |>
  mutate(percent = n / sum(n)) |>
  #filter(financial_satisfaction == "Not Satisfied At All") |>
  #mutate(satisfied = 1 - percent) |>
  ggplot(aes(x = year, y = percent, color = financial_satisfaction )) +
  geom_line() +
  geom_smooth(method=lm, se=FALSE) + 
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(cohort_band), nrow = 3, ncol = 3) +
  theme(legend.position="bottom")
```

@@

### Financial Compare

```{r}

#| message: false
#| echo: false
#| warning: false

@@

## Discussion

## Conclusion

## Reference

>>>>

combined_data$family_income_bands =
  factor(combined_data$family_income_bands,
         levels = c(
           "<$15K",
           "$15K-$25K",
           "$25K-$35K",
           "$35K-$50K",
           "$50K-$75K",
           "$75K-$100K",
           ">$100K"
           )
         )

@@

# To Do

@@

-   calculating % ... over the year for graph - DONE

@@

# Introduction

@@

# Data

@@

## Gaps

@@

## Translations

@@

## Affordances: New Experiments

@@

## Impact on our study

@@

# Findings

## Financial Satisfaction

@@

Financial satisfaction - does money make you more financially satisfied? oh yea.

```{r}
#| message: false
#| echo: false
#| warning: false
#| 
survey_data_2021 |>
  filter(!is.na(family_income_bands), !is.na(financial_satisfaction)) |>
  ggplot(aes(x = financial_satisfaction, group = family_income_bands)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage of response") +
  xlab("Financial Satisfaction") +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position="none") +
  facet_grid(~family_income_bands)
```

@@

financial_satisfaction_across_years_by_cohort =
  combined_data |>
    select(year, cohort_band, financial_satisfaction) |>
    group_by(year, cohort_band) |>
    count(financial_satisfaction)

financial_satisfaction_across_years_by_cohort |>
  filter(!is.na(financial_satisfaction)) |>
  filter(!(is.na(cohort_band))) |>
  mutate(percent = n / sum(n)) |>
  ggplot(aes(x = year, y = percent, color = financial_satisfaction )) +
  geom_line() +
  geom_smooth(method=lm, se=FALSE) + 
  scale_y_continuous(labels=scales::percent) +
  facet_wrap(vars(cohort_band), nrow = 3, ncol = 3) +
  theme(legend.position="bottom")
```

## Social Class

@@

survey_data_2021 |>
  filter(!is.na(family_income_bands), !is.na(social_class)) |>
  ggplot(aes(x = social_class, group = family_income_bands)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage of response") +
  xlab("Financial Satisfaction") +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(legend.position="none") +
  facet_grid(~family_income_bands)
```

The variable *realinc* has only \~30 values - probably something to do with bands that are in the raw survey data

survey_data_2021 |>
  filter(!is.na(social_class)) |>
  ggplot(aes(x = social_class, y = realinc)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.3, width = 0.10, height = 0)
  #geom_point(alpha = 0.2) +
  #geom_violin()
```

## Financial Compare

@@

# Discussion

# Conclusion

# Reference
